Cluster Dynamics with HETDEX at z < 0.5 - I: Simulated Performance, Mass Recovery, and Limits to Cosmology

### 2017-01-11 paper1.tex
first set of casey comments
more to come

% MNRAS is set in Times font. If you don't have this installed (most LaTeX
% installations will be fine) or prefer the old Computer Modern fonts, comment
% out the following line
\usepackage{newtxtext,newtxmath}
\usepackage{times}
% Depending on your LaTeX fonts installation, you might get better results with one of these:
% \usepackage{mathptmx}
% \usepackage{txfonts}

@@

\subsection{Conditional {\rm[\ion{O}{II}]} Flux Probability Distribution Functions}\label{sec: oii luminosity}
We use the SDSS DR12 \citep{Alam2015} catalogs to assign [\ion{O}{II}] emission line strengths to the galaxies in the Buzzard catalog. We use 503,113 objects classified as galaxies selected over $z = 0.02 - 0.2$ with {\sc zwarning $=0$} and a measured [\ion{O}{II}] line flux signal-to-noise of five. Figure~\ref{fig: oii sdss} shows the color-magnitude diagram (CMD) of $M_r$ and $g-r$ for these galaxies, and the following SQL query selects the appropriate galaxies:
\begin{lstlisting}[language=SQL]
SELECT GAL.objid, 
       GAL.u, 
       GAL.err_u, 
       GAL.g, 
       GAl.err_g, 
       GAL.r, 
       GAL.err_r, 
       GAL.i, 
       GAl.err_i, 
       GAL.z, 
       GAL.err_z, 
       g.oii_3726_flux, 
       g.oii_3726_flux_err, 
       s.z 
FROM   galaxy AS GAL 
       JOIN specobj AS s 
         ON s.bestobjid = GAL.objid 
       JOIN galspecline AS g 
         ON g.specobjid = s.specobjid 
WHERE  oii_3726_flux > oii_3726_flux_err * 5 
       AND oii_3726_flux_err > 0 
       AND s.class = 'GALAXY' 
       AND s.zwarning = 0 
\end{lstlisting}

@@

\subsection{HETDEX}\label{sec: hetdex}
\begin{figure}
\includegraphics[width=\columnwidth]{figures/pointings.pdf} 
	\caption[HETDEX pointing strategy.]{\emph{Top:} Representative observation tiling scheme for the HETDEX $16' \times 16'$ pointings over a small region of the sky. \emph{Bottom:} The simplified tiling pattern used in this study. In both schemes, the dashed octagons approximate the size of a single observation. Each observation consists of the 78 VIRUS IFUs, represented by the turquoise squares in the bottom panel. Inside each IFU HETDEX will achieve near complete coverage through three dithers. See the text for more details.} 
	\label{fig: ifu layout} 
\end{figure}

@@

The entire HETDEX survey will cover 420 \degsq\ with a 1/4.5 filling factor over two fields: a $\sim 300$ \degsq\ northern field, and a $\sim 140$ \degsq\ equatorial region. The spectral coverage allows for the detection of [\ion{O}{II}] ($\lambda\lambda 3727,3729$) emitters to $z\sim 0.5$ and Ca H ($\lambda 3968.5$) and K ($\lambda 3933.7$) absorption features to $z\sim 0.4$. The $10 \sigma$ detection threshold for spectral features will be $3.5\times10^{-17}$ \ergscm\ at 5000 \AAA, or equivalently, $g = 21.9$ mag for continuum objects.

@@

\subsection{Mock Observations}\label{sec: observations}
When selecting galaxies from the Buzzard catalog we assume an observation for all galaxies laying within a turquoise, IFU square in Figure~\ref{fig: ifu layout}. In practice, this is achieved by three dither positions at each pointing. Galaxies which lie between the IFUs are missed, as well as the galaxies which lie between the pointings, as there is no overlap between one pointing and the next. We use a pointing pattern which differs slightly from the expected final HETDEX observing pattern. See Figure~\ref{fig: ifu layout} for an illustration of the difference. To cover the 398.49 \degsq\ field of the Buzzard catalog we require 5370 pointings where 0.015 \degsq\ of each pointing is covered by an IFU. The total area of the sky covered by an IFU is 80.80 \degsq\ which gives a filling factor of 1/4.65, slightly (about 3\%) decreased from the expected filling factor of 1/4.5.

In this work we consider two separate observing strategies, Targeted and Survey. The Targeted observations use ``direct'' observations where each cluster is targeted individually, and every cluster member galaxy is assumed to be observed. The Survey observations mimic the HETDEX observation pattern across the sky, where no cluster is directly targeted and not all cluster member galaxies are observed. Both of these observations have HETDEX-like galaxy detection thresholds (described in the previous subsection), so while a galaxy may be observed, a redshift will only be measured if the galaxy satisfies the continuum brightness or emission line flux limits for the HETDEX survey. For comparison we also include a Perfect observation, in which we assume all galaxies in a field are observed and all redshifts measured. This provides a baseline where the cluster properties are calculated under the best possible conditions and against which we can compare the results of the ``Targeted'' and ``Survey'' observing strategies.

\section{Recovery of Parameters}\label{sec:recovery}
In the following sections, we assume that we know a priori which galaxies belong to each individual cluster. So while our observations may include many field galaxies which are not belonging to the cluster in question, we exclude those galaxies during the analysis of the cluster parameters. Cluster membership is a critical issue which must be addressed when utilizing real observations. To that end, we assay a small sample of real galaxy clusters in a follow up work (Boada \etal\ in Preparation).

@@

In simple terms, the cluster redshift is the mean of the redshifts of all galaxies associated with the cluster, where the mean is the first moment of the velocity (redshift) distribution function $P(z)$. In practice, the first moment is strongly subject to outliers, so we rely instead on the biweight location estimator \citep{Beers1990} through\footnote{Implemented as part of the {\sc astLib} Python library \citep{astlib}. See \hbox{\url{http://astlib.sourceforge.net}}}:
\begin{equation}
z_c = z_{med} + \frac{\sum_{|u_i| < 1} (z_i - M)(1-u_i^2)^2}{\sum_{|u_i| < 1}(1-u_i^2)^2}
\end{equation}
where $z_i$ are the individual redshifts, $z_{med}$ is the median redshift and $u_i$ is given by:
\begin{equation}
	u_i = \frac{(z_i - M)}{C\,\mathrm{MAD}}.
\end{equation}
MAD is the median absolute deviation, also defined in \cite{Beers1990}, and $C$ is the a tuning constant. We choose $C=6$ (the suggested value) which balances computational speed and location accuracy. 
% Although this work assumes that we know each galaxy's redshift to infinite precision, in practice, we find a simple weighted mean provides a reliable estimate of $z_c$ when there are uncertainties on the individual galaxy redshifts.

\subsection{Line-of-Sight Velocity Dispersion}\label{sec: LOSVD}
We calculate the LOSV to each galaxy, where
\begin{equation}
	\mathrm{LOSV} = c\frac{z - z_c}{1+z_c}
\end{equation}
and $c$ is the speed of light, $z$ is the redshift of the individual galaxy, and $z_c$ is the overall cluster redshift described in the previous subsection.

@@

\subsubsection{Other Estimates of Dynamical Mass -- Introduction}
In the following subsections we use two methods to predict the mass of a cluster based on other observables. Often the cluster mass is estimated based on a single observable, X-ray temperature, LOSVD, richness and others (see Section~\ref{sec: Introduction} for referenced examples). Here we combine many observables to attempt to correct the mass inferred solely from the velocity dispersion. The first method is traditional ``probability based'' where we marginalize over a series of observables to find the most probable cluster mass. The second is based on a machine learning (ML) algorithm which attempts to infer the relationship between the observables and the desired output, the cluster mass. Both of these methods are examples of supervised learning algorithms where the relationship between the observable parameters and the target parameter (the cluster mass) are both known.

As with any predictive analysis it is important to test the model on data that the model has not seen before. This prevents over-fitting. In the following subsections we take all of the observed clusters, our full sample, split them, and generate a \emph{training} and \emph{testing} set \citeeg{Ripley2007, Xu2013, Ntampaka2015, Ntampaka2015a, Acquaviva2016}. Traditionally, the training set is a set of data used to infer possibly predictive relationships. The test set of data is then used to assess the correctness of the predictive relationship. Our data is randomly split into 70\% training and 30\% testing. We follow the ML convention and refer to the individual clusters in each set as a ``sample'', and the parameters associated with the cluster ($z$, LOSVD, mass, etc.) as ``features''.

@@

\begin{figure*}
	\includegraphics[width=\textwidth]{figures/prob_example.pdf} 
	\caption[Illustration of the probability based cluster mass prediction method.]{Illustration of the probability based cluster mass prediction method. \emph{Left}: The two dimensional posterior probability distribution of LOSVD and redshift used to determine the correct cluster mass. The pink and green rectangles show the locations of two example galaxy clusters used to create the conditional probability distribution of the mass, $P(\log\ M_{200c}|z, \mathrm{Log}\, \sigma)$. \emph{Right}: The conditional probability distribution of the cluster mass for the two example galaxies. See text for a complete description.}
	\label{fig: probability corner} 
\end{figure*}

@@

\section{Results}\label{sec:results}
Here we explore the cluster member recovery rate and mass estimates for the two observing strategies, Targeted, and Survey. Targeted observations are direct observations of a cluster where each cluster member galaxy, above the detection thresholds (see Section \ref{sec: observations}), is observed. Survey observations mimic the HETDEX observation strategy such that no cluster is directly observed, and only the cluster member galaxies above the detection threshold and within an IFU (see Figure \ref{fig: ifu layout}) are observed.  We discuss the accuracy of cluster dynamical mass derived from both the power law scaling relation (see Equation \ref{eq:power law}) and through the probability and ML methods. We also compare the results from the Targeted and Survey observing strategies to the results of a ``Perfect'' survey, where the redshift of each galaxy, regardless of observational limits, in the cluster is known perfectly.

@@

For the Targeted observations, shown in the left panel of Figure~\ref{fig: recovery}, the pattern of decreasing recovery fraction as a function of redshift (y-direction) is due to the observational limits imposed. Because the redshift success rate of HETDEX is limited by apparent magnitude, we expect to recover fewer galaxies at higher redshift, where the galaxies are often below our $5\sigma$ detection threshold. For example, we tested this by constructing an artificial HETDEX-like survey, limited by volume for all galaxies with $M_g < -11$. In this case, our recovery fraction increases to $>70$\%, which shows that the flux limit is dominating the (lower) recovery of our flux-limited survey.

For the recovery fraction as a function of true cluster mass (x-direction), we find a general decrease in the recovery fraction of member galaxies with increasing cluster mass. This  is entirely a result of the flux limited survey (see previous paragraph). Because there are few high mass ($M_{200c}>5\times10^{14}$ \Msol) clusters, many of which are at moderately high redshift, the higher redshift cluster members suffer from the limiting apparent magnitude and suppress the recovery fraction at fixed mass. If we were to limit the Survey to $z<0.2$ we find the recovery fraction of clusters, across all masses, increases substantially, and we find a much more consistent detection fraction across all masses. However, doing so limits severely the number of clusters at masses greater than $10^{14}$ \Msol.

@@

The recovery fractions in Figure~\ref{fig: recovery} are an outcome of the magnitude limit and [\ion{O}{II}] line-flux limit of the survey. For Perfect observations, we would detect all members across all cluster masses and redshifts. Recovery fractions of clusters located a the low end of the redshift distribution will improve the most by follow-up targeted observations. But generally, the number of members observed (and subsequently more accurate cluster mass estimates) will benefit from follow-up observations regardless of the redshift. So follow-up observations should be tailored to the specific science goal.

@@

Because it represents the best possible scenario, the Perfect knowledge observations should serve as a baseline to compare the power law based, probability based and ML cluster mass recovery methods. And, while there are many possible metrics to evaluate performance, we compute two: the average bias (given in Table \ref{tbl:mass bias})
\begin{equation}\label{eqn: bias}
\mathrm{\mu_{bias}}(y,y_{pred}) = \frac{1}{N} \sum_{i=1}^N (y_{pred,i} - y_i).
\end{equation}
where $y$ are the true values and $y_{pred}$ are the predicted values, and the scatter about the bias (given in Table \ref{tbl:mass scatter})
\begin{equation}\label{eqn: scatter}
	\sigma_{bias}(y,y_{pred}, \mu_{bias}) = \bigg{[}\frac{1}{N-1} \sum_{i=1}^N (y_{pred,i} - y_i - \mu_{bias})^2 \bigg{]}^{1/2}
\end{equation}
with $N$ clusters in a given bin. Both metrics evaluate how closely the ensemble of predicted cluster masses are to the true cluster masses.

@@

For the Targeted and Survey observations the power law predicted cluster masses give $\mu_{bias} =0.135\pm{0.003}$ dex, $\sigma_{bias} = 0.370\pm{0.002}$ and $\mu_{bias} =0.148\pm{0.008}$ dex, $\sigma_{bias} = 0.324\pm{0.006}$ , respectively. So for the clusters that we detect with Survey observations, we obtain similar levels of accuracy as to the Targeted observations, on the average. This does not mean that the Survey observations cannot be improved by Targeted observations. In fact, when comparing only the galaxies which overlap between the two samples the bias and scatter of the Targeted observations is significantly decreased as more cluster member galaxies are detected, better sampling the LOSVD probability distribution function. The Targeted observations perform similarly on the average because many lower mass clusters are included in the sample, increasing the bias of the overall sample.

>>>>

% MNRAS is set in Times font. If you don't have this installed (most LaTeX
% installations will be fine) or prefer the old Computer Modern fonts, comment
% out the following line
%\usepackage{newtxtext,newtxmath}
\usepackage{times}
% Depending on your LaTeX fonts installation, you might get better results with one of these:
% \usepackage{mathptmx}
% \usepackage{txfonts}

@@

\subsection{Conditional {\rm[\ion{O}{II}]} Flux Probability Distribution Functions}\label{sec: oii luminosity}
We use the SDSS DR12 \citep{Alam2015} catalogs to assign [\ion{O}{II}] emission line strengths to the galaxies in the Buzzard catalog. We use 503,113 objects classified as galaxies selected over $z = 0.02 - 0.2$ with {\sc zwarning $=0$} and a measured [\ion{O}{II}] line flux signal-to-noise of at least five. Figure~\ref{fig: oii sdss} shows the color-magnitude diagram (CMD) of $M_r$ and $g-r$ for these galaxies, and the following SQL query selects the appropriate galaxies:
\begin{lstlisting}[language=SQL]
SELECT GAL.objid, 
       GAL.u, 
       GAL.err_u, 
       GAL.g, 
       GAl.err_g, 
       GAL.r, 
       GAL.err_r, 
       GAL.i, 
       GAl.err_i, 
       GAL.z, 
       GAL.err_z, 
       g.oii_3726_flux, 
       g.oii_3726_flux_err, 
       s.z 
FROM   galaxy AS GAL 
       JOIN specobj AS s 
         ON s.bestobjid = GAL.objid 
       JOIN galspecline AS g 
         ON g.specobjid = s.specobjid 
WHERE  oii_3726_flux > oii_3726_flux_err * 5 
       AND oii_3726_flux_err > 0 
       AND s.class = 'GALAXY' 
       AND s.zwarning = 0 
\end{lstlisting}

@@

\subsection{HETDEX}\label{sec: hetdex}
\begin{figure}
\includegraphics[width=\columnwidth]{figures/pointings.pdf} 
	\caption[HETDEX pointing strategy.]{\emph{Top:} Representative observation tiling scheme for the HETDEX $16' \times 16'$ pointings over a small region of the sky. \emph{Bottom:} The simplified tiling pattern used in this study. In both schemes, the dashed octagons approximate the size of a single observation. Each observation consists of the 78 VIRUS IFUs, represented by the turquoise squares in the bottom panel shown for one of the HETDEX pointings. Inside each IFU HETDEX will achieve near complete coverage through three dithers. See the text for more details.} 
	\label{fig: ifu layout} 
\end{figure}

@@

The entire HETDEX survey will cover 420 \degsq\ with a 1/4.5 filling factor over two fields: a $\sim 300$ \degsq\ northern field, and a $\sim 140$ \degsq\ equatorial region. The spectral coverage allows for the detection of [\ion{O}{II}] ($\lambda\lambda 3727,3729$) emitters to $z\sim 0.5$ and Ca H ($\lambda 3968.5$) and K ($\lambda 3933.7$) absorption features to $z\sim 0.4$. The $10 \sigma$ detection threshold for emission spectral features will be $3.5\times10^{-17}$ \ergscm\ at 5000 \AAA, or equivalently, $g = 21.9$ mag for continuum objects.

@@

\subsection{Mock Observations}\label{sec: observations}
When selecting galaxies from the Buzzard catalog we assume an observation for all galaxies laying within a turquoise, IFU square in Figure~\ref{fig: ifu layout}. In practice, this is achieved by three dither positions at each pointing. Because of the 1:3 fill factor, many galaxies will not receive spectroscopic coverage, including galaxies that lie between IFUs within a pointing, as well as galaxies between pointings. We use a pointing pattern which differs slightly from the expected final HETDEX observing pattern. See Figure~\ref{fig: ifu layout} for an illustration of the difference. To cover the 398.49 \degsq\ field of the Buzzard catalog we require 5370 pointings where 0.015 \degsq\ of each pointing is covered by an IFU. The total area of the sky covered by an IFU is 80.80 \degsq\ which gives a filling factor of 1/4.65, slightly (about 3\%) decreased from the expected filling factor of 1/4.5.

We measure cluster velocity dispersions using three different spectroscopic observing patterns. We consider three separate observing strategies, Targeted, Survey and Perfect. The Targeted observations use ``direct'' observations where each cluster is targeted individually with a 1:1 fill factor such that every cluster member galxay is assumed to be observed. The Survey observations mimic the HETDEX observation pattern across the sky, where no cluster is directly targeted. Each cluster is observed with the 1/4.5 fill factor, such that not all cluster member galaxies are observed. Both of these observations have HETDEX-like galaxy detection thresholds (described in the previous subsection), so while a galaxy may be observed, a redshift will only be measured if the galaxy satisfies the continuum brightness or emission line flux limits for the HETDEX survey. For comparison we also include a Perfect observation, in which we assume all galaxies in a field are observed and all redshifts measured. This provides a baseline where the cluster velocity dispersion is calculated under the best possible conditions and against which we can compare the results of the ``Targeted'' and ``Survey'' observing strategies.

\section{Recovery of Parameters}\label{sec:recovery}
In the following sections, we assume that we know \textit{a priori} which galaxies belong to each individual cluster. So while our observations may include many field galaxies which do not belong to the cluster in question, we exclude those galaxies during the analysis of the cluster parameters. Cluster membership is a critical issue which must be addressed when utilizing real observations. To that end, we assay a small sample of real galaxy clusters in a follow up work (Boada \etal\ in Preparation).

@@

In simple terms, the cluster redshift is the mean of the redshifts of all galaxies associated with the cluster, where the mean is the first moment of the velocity (redshift) distribution function $P(z)$. In practice, the first moment is strongly subject to outliers, so we rely instead on the biweight location estimator \citep{Beers1990} through\footnote{Implemented as part of the {\sc astLib} Python library \citep{astlib}. See \hbox{\url{http://astlib.sourceforge.net}}}:
\begin{equation}
z_c = z_{med} + \frac{\sum_{|u_i| < 1} (z_i - M)(1-u_i^2)^2}{\sum_{|u_i| < 1}(1-u_i^2)^2}
\end{equation}
where $z_i$ are the individual redshifts, $z_{med}$ is the median redshift and $u_i$ is given by:
\begin{equation}
	u_i = \frac{(z_i - M)}{C\,\mathrm{MAD}}.
\end{equation}
MAD is the median absolute deviation, also defined in \cite{Beers1990}, and $C$ is the a tuning constant. We choose $C=6$ (the \citealt{Beers1990} suggested value). 
% Although this work assumes that we know each galaxy's redshift to infinite precision, in practice, we find a simple weighted mean provides a reliable estimate of $z_c$ when there are uncertainties on the individual galaxy redshifts.

\subsection{Line-of-Sight Velocity Dispersion}\label{sec: LOSVD}
We calculate the LOSV, $v_i$, to each galaxy, where
\begin{equation}
	v_i = c\frac{z - z_c}{1+z_c}
\end{equation}
and $c$ is the speed of light, $z$ is the redshift of the individual galaxy, and $z_c$ is the overall cluster redshift described in the previous subsection.

@@

\subsubsection{Other Estimates of Dynamical Mass -- Introduction}
In the following subsections we use two methods to predict the mass of a cluster based on other observables. Often the cluster mass is estimated based on a single observable, \eg\ X-ray temperature, LOSVD, richness and others (see Section~\ref{sec: Introduction} for referenced examples). Here we combine many observables to attempt to correct the mass inferred solely from the velocity dispersion. The first method is traditional ``probability based'' where we marginalize over a series of observables to find the most probable cluster mass. The second is based on a machine learning (ML) algorithm which attempts to infer the relationship between the observables and the desired output, the cluster mass. Both of these methods are examples of supervised learning algorithms where the relationship between the observable parameters and the target parameter (the cluster mass) are both known.

As with any predictive analysis it is important to test the model on data that the model has not seen before. This prevents over-fitting. In the following subsections we take all of the simulated cluster observations, split them, and generate a \emph{training} and \emph{testing} set \citeeg{Ripley2007, Xu2013, Ntampaka2015, Ntampaka2015a, Acquaviva2016}. Traditionally, the training set is a set of data used to infer possibly predictive relationships. The test set of data is then used to assess the correctness of the predictive relationship. Our simulated observations are randomly split into 70\% training and 30\% testing. We follow the ML convention and refer to the individual clusters in each set as a ``sample'', and the parameters associated with the cluster ($z$, LOSVD, mass, etc.) as ``features''.

@@

\begin{figure*}
	\includegraphics[width=\textwidth]{figures/prob_example.pdf} 
	\caption[Illustration of the probability based cluster mass prediction method.]{Illustration of the probability based cluster mass prediction method. \emph{Left}: The two dimensional posterior probability distribution of LOSVD and redshift used to determine the correct cluster mass. The pink and green rectangles show the locations of two example galaxy, $\vec{x}_1 = \{z=0.16,\ \log~\sigma=2.4\}$ and $\vec{x}_2 = \{z=0.36,\ \log~\sigma=2.7\}$, clusters used to create the conditional probability distribution of the mass, $P(\log\ M_{200c}|z, \mathrm{Log}\, \sigma)$. \emph{Right}: The conditional probability distribution of the cluster mass for the two example galaxies. See text for a complete description.}
	\label{fig: probability corner} 
\end{figure*}

@@

\section{Results}\label{sec:results}
Here we explore the cluster member recovery rate and mass estimates for the two observing strategies, Targeted, and Survey. Targeted observations are direct observations of a cluster where each cluster member galaxy, above the detection thresholds (see Section \ref{sec: observations}), is observed. Survey observations mimic the HETDEX observation strategy such that no cluster is directly observed, and only the cluster member galaxies above the detection threshold and within an IFU (see Figure \ref{fig: ifu layout}) are observed.  We discuss the accuracy of cluster dynamical mass derived from both the power law scaling relation (see Equation \ref{eq:power law}) and through the probability and ML methods. We also benchmark the results from the Targeted and Survey observing strategies to the results of a ``Perfect'' survey, where the redshift of each galaxy, regardless of observational limits, in the cluster is known perfectly.

@@

For the Targeted observations, shown in the left panel of Figure~\ref{fig: recovery}, the decreasing recovery fraction as a function of redshift (y-direction) is due to the observational limits of the survey. Because the redshift success rate of HETDEX is limited by apparent magnitude, we expect to recover fewer galaxies at higher redshift, where the galaxies are often below our $5\sigma$ detection threshold. We tested this by constructing an artificial HETDEX-like survey, limited by volume for all galaxies with $M_g < -11$. In this case, our recovery fraction increases to $>70$\%, which shows that the flux limit is dominating the (lower) recovery of our flux-limited survey.

For the recovery fraction as a function of true cluster mass (x-direction), we find a general decrease in the number of member galaxies with increasing cluster mass. This  is entirely a result of the flux limited survey (see previous paragraph). Because there are few high mass ($M_{200c}>5\times10^{14}$ \Msol) clusters, many of which are at moderately high redshift, the higher redshift cluster members suffer from the limiting apparent magnitude and suppress the recovery fraction at fixed mass. If we were to limit the Survey to $z<0.2$ we find the recovery fraction of clusters, across all masses, increases substantially, and we find a much more consistent detection fraction across all masses. However, doing so limits severely the number of clusters at masses greater than $10^{14}$ \Msol because of the limited survey volume.

@@

The recovery fractions in Figure~\ref{fig: recovery} are an outcome of the magnitude limit and [\ion{O}{II}] line-flux limit of the survey. For Perfect observations, we would measure redshifts for all members across all cluster masses and redshifts. Recovery fractions of clusters located a the low end of the redshift distribution will improve the most by follow-up targeted observations. But generally, the number of members observed (and subsequently more accurate cluster mass estimates) will benefit from follow-up observations regardless of the redshift, which can be tailored for the specific scientific goal.

@@

Because it represents the best possible scenario, the Perfect knowledge observations should serve as a baseline against which to compare all other methods. And, while there are many possible metrics to evaluate performance, we compute two: the average bias (given in Table \ref{tbl:mass bias})
\begin{equation}\label{eqn: bias}
\mathrm{\mu_{bias}}(y,y_{pred}) = \frac{1}{N} \sum_{i=1}^N (y_{pred,i} - y_i).
\end{equation}
where $y$ are the true values and $y_{pred}$ are the predicted values, and the scatter about the bias (given in Table \ref{tbl:mass scatter})
\begin{equation}\label{eqn: scatter}
	\sigma_{bias}(y,y_{pred}, \mu_{bias}) = \bigg{[}\frac{1}{N-1} \sum_{i=1}^N (y_{pred,i} - y_i - \mu_{bias})^2 \bigg{]}^{1/2}
\end{equation}
with $N$ clusters in a given bin. Both metrics evaluate how closely the ensemble of predicted cluster masses are to the true cluster masses.

@@

For the Targeted and Survey observations the power law predicted cluster masses give $\mu_{bias} =0.135\pm{0.003}$ dex, $\sigma_{bias} = 0.370\pm{0.002}$ dex and $\mu_{bias} =0.148\pm{0.008}$ dex, $\sigma_{bias} = 0.324\pm{0.006}$ dex, respectively. So for the clusters that we detect with Survey observations, we obtain similar levels of accuracy as to the Targeted observations, on the average. This does not mean that the Survey observations cannot be improved by Targeted observations. In fact, when comparing only the galaxies which overlap between the two samples the bias and scatter of the Targeted observations is significantly decreased as more cluster member galaxies are detected, better sampling the LOSVD probability distribution function. The Targeted observations perform similarly on the average because many lower mass clusters are included in the sample, increasing the bias of the overall sample.
